---
title: "Exercise-1"
author: "Himanshu Mayank"
date: "2023-03-07"
output: pdf_document
---
**Loading the connections dataset**
```{r Loading the data}
library("tidyverse")
library("igraph")
csv = read_csv('Connections.csv')
csv
View(csv)
attach(csv)
df = csv %>% mutate(Company = str_trim(Company)) %>% drop_na(Company)  
head(df,10)
```
**Filtering out the data and choosing  top 5 companies   my connections belong to **
```{r Filtering top 5 companies}
library(dplyr)

# group the data by Company and count the frequency
company_count <- df %>% 
  group_by(Company) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

# get the top 10 companies by frequency
top_5_companies <- company_count$Company[1:5]
head(top_5_companies,10)
```

```{r Filtering the data}
# filter the data for only the top 10 companies
csv <- df %>% 
  filter(Company %in% top_5_companies)
csv$`Last_Name` <- substr(csv$`Last Name`, 1, 1)
csv <- csv %>% 
  slice_sample(n = 50, replace = TRUE) 
head(csv,10)
```


**Counting the number of connections from the sample for each company.For simplicity top 5 organisations is selected **

```{r company}
count = csv %>% count(Company, sort=TRUE)
count
```



**Creating a new column with the first name with the last name initials**

```{r counting}
csv$last_initial <- substr(csv$`Last Name`, 1, 1)
csv$Full_Name <- paste(csv$`First Name`, csv$last_initial, sep = " ")
new_csv <- csv[, c("Full_Name", "Company")]
```
**Create a new data frame called nodes by selecting only unique Full_Name values from the new_csv data frame, and then adding a new column called id with unique identifier values for each row.**

```{r creating nodes}
nodes <- new_csv %>% distinct(Full_Name)
nodes <- nodes %>% rowid_to_column('id')
nodes
copy <- new_csv
colnames(copy) <- paste(colnames(copy), "2", sep="_")
```
**Create a new data frame called cross by taking the cross-product of the new_csv and copy data frames, resulting in every possible combination of rows from both data frames.**
**A new data frame called edges is created  by filtering the cross data frame to include only rows where the Company and Company_2 columns are equal and the Full_Name and Full_Name_2 columns are not equal.**

```{r creating cross}
cross <- tidyr::crossing(new_csv, copy, .name_repair="minimal")
edges <- filter(cross, cross$Company == cross$Company_2 & cross$Full_Name != cross$Full_Name_2)
edges <- edges %>% select(Full_Name, Company, Full_Name_2, Company_2)
edges <- edges %>% 
  left_join(nodes, by = c("Full_Name" = "Full_Name")) %>% 
  rename(node_1 = id)
edges <- edges %>% 
  left_join(nodes, by = c("Full_Name_2" = "Full_Name")) %>% 
  rename(node_2 = id)
edges <- select(edges, node_1, node_2)
head(edges,10)
```

**Creating a network from the given nodes and edges**
```{r importing the graph libraries}
library("tidygraph")
library("ggraph")
network <- tbl_graph(nodes=nodes, edges=edges, directed=FALSE)
network
```
**Plotting the graph. People from same organisation will share an edge **
```{r plotting}
ggraph(network) +
geom_edge_link() +
geom_node_point() +
geom_node_text(aes(label=Full_Name), repel=TRUE) +
theme_graph()
```
```{r plotting -2}
graph <- graph_from_data_frame(edges, vertices = nodes, directed = FALSE)
V(graph)$name <- nodes$Full_Name
par(mar = rep(1, 4))
options(repr.plot.width = 100, repr.plot.height = 1000)
plot(graph, vertex.size = 7, vertex.color = "lightpink", vertex.label.cex = 0.6, edge.color = "gray", edge.width = 2, edge.length=500000, vertex.dist = 50)
```



**Intuitively we can see that we get 5 different graphs ,one for each organisation since the data was filtered and sampled for top 5 ornagisation** 